HUME: Human UCCA-based Machine-Translation Evaluation

### 2016-03-06 paper/main.tex
xxx

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}

@@

\begin{abstract}
 This document contains instructions for preparing ACL 2016 submissions and camera-ready
  manuscripts.  The document itself conforms
  to its own specifications, and is therefore an example of what
  your manuscript should look like.  Papers are required to conform to
  all the directions reported in this document.  
By using the provided \LaTeX\ and \BibTeX\ styles ({\small\tt acl2016.sty}, {\small\tt acl2016.bst}), the required formatting will be enabled by default.
\end{abstract}

\section{ Human Semantic Evaluation}
\label{sec:sem-eval:human}
We focus on producing high accuracy machine translation systems, but common 
automatic MT metrics are not able to directly capture accuracy. Even previously suggested methods
for using humans to evaluate accuracy are highly problematic. We aim to  develop a human evaluation method 
which is reliable and affordable and apply it to the MT prototypes. 
%This 
The
work described
in this section relates to 
%the 
task
\emph{T5.2: Human semantic evaluation}.
% defined in the description of action.

@@

\bibliography{mt}
\bibliographystyle{acl2016}

>>>>

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{subfigure}
\usepackage{pgfplotstable}
\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\oa}[1]{\footnote{\color{red} #1}}

@@

\begin{abstract}

  Semantic evaluation of Machine Translation (MT) systems has become
  a necessity, given recent interest in semantics-aware MT systems.
  We present a novel human semantic evaluation measure for MT, Human
  UCCA-based MT evaluation (HUME), building on the UCCA semantic representation scheme.
  Making progress over previous work, the proposed measure takes into account
  a wider range of semantic phenomena and does not rely on semantic annotation
  of the MT output, whose interpretation is often unclear. 
  We experiment with four language pairs, demonstrating the broad applicability of
  the measure, as well as its reliability, reflected by the inter-annotator agreement
  rates.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}

Human judgement is the central, and perhaps ultimate, criterion for estimating the
quality of an MT system.
Nevertheless, common measures for MT evaluation, such as adequacy and frequency judgements
or the relative ranking of several possible translations, are problematic in two ways.
First, as the quality of translation is determined by multiple factors, it is difficult
to assign a single number that quantifies the quality of the entire sentence, as is reflected
by the diminishing inter-annotator agreement rates of human ranking measures
as a function of the sentence length \cite{Bojar:2011}.
Second, a global quality score does not localize the errors in the translation output,
and hence cannot inform measures to overcome these errors.
This problem can be addressed by using scores that decompose over
the sub-parts of the sentence. 
However, common decompositions into n-grams or even individual words, as employed by the
popular BLEU \cite{Papineni:2002} and METEOR measures \cite{Banerjee:2005},
are most suitable for evaluating shallow MT approaches and are
less instructive for more structurally-aware methods, which are at
the forefront of MT research today.

These difficulties have motivated the definition of a human measure that decomposes over
the semantic structure of the sentence, rather than its n-grams. The most notable attempt of
this brand is the HMEANT
measure \cite{LoWu2010,lo2011structured,LoWu2011b,LoWu2012}, which quantifies the
similarity the verbal argument structures of the translation output and reference.
While appealing in addressing the two major shortcomings
detailed above, HMEANT is unable to capture semantic differences which do not show up in
the verb-argument structure, including several very frequent phenomena, such as
inter-clause linkage, nominalizations and copula clauses (see \secref{sec:hmeant_comp}).
Another shortcoming of MEANT lies with its reliance on semantically annotating MT output,
which is often unintelligible. Finally, measures based on a comparison to a reference translation
is necessarily incomplete, given the huge number of reasonable translations
a sentence may have \cite{dryer_marcu:12}.

In this work we propose the Human UCCA-based MT Evaluation ({\it HUME}) metric,
a human evaluation measure that decomposes over the sentence's semantic units.
The units are defined according to the 
UCCA scheme \cite{abend2013universal}, an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and the inter-relations between them.
In contrast to previous proposals of semantic MT evaluation,

HUME operates by aggregating human assessments of the translation quality of the different
semantic units in the source sentence.
In thus only requires the semantic annotation of the source sentence, thus avoiding the 
annotatation of machine-generated text, a difficult if not ill-defined task.
By basing the measure on a direct comparison
of the source and translation we avoid the difficulties engendered by using
reference translations, albeit at the cost of imposing the additional requirement
that the evaluator be proficient in both the source and target languages.
See \secref{sec:} for a discussion of HUME's advantages realative to other measures.

We conduct experiments with four language pairs, English-German, English-Polish,
English-Romanian and English-Czech, and report efficiency (time of annotation) and
inter-annotator agreement scores, as well as qualitative comparison of resulting
HUME scores and BLEU, and crowd-sourced adequacy judgements. Results show that HUME obtains 
agreements which are in par with standard sentence-level ranking measures, but unlike with them,
the agreement does not diminish with the sentence length.

\oa{summary of contribution}

\oa{what is the purpose of the BLEU binning?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}\label{sec:background}

% MT evaluation
\paragraph{MT Evaluation.}

% semantic representation
\paragraph{Semantic Representation.}
Much interest has been devoted recently to broad-coverage semantic analysis of text.
The Abstract Meaning Representation (AMR) scheme \cite{banarescu2013abstract}
shares much of UCCA's motivation for defining a more complete semantic annotation.
However, it is not optimal for our purposes as they do not ground the semantic symbols
in the text, thus not straightwardly allowing a decomposition of the sentence into sub-units,
and are more fine-grained and consequently more difficult to annotate.

Several approaches have been proposed for grounded semantic representations,
generally viewing semantic structures as bi-lexical dependencies. Examples include
the Prague Treebank tectogrammatical layer \cite{hajic2012announcing}, as well as dependencies derived
from Minimal Recursion Semantics representations \cite{oepen2006discriminant}.
Despite their appeal as deep and intuitive means for semantic representations,
these approaches also provide fine-grained distinctions and require linguistic expertise to annotate.
%\newcite{Basile:12} attempted to make some aspects of the semantic annotation more accessible,
%but to our knowledge no results of this brand have been reported.

UCCA (Universal Conceptual Cognitive Annotation) is a natural selection for purposes of MT evaluation
for a number of reasons. 
First, it diverges from the above approaches in representing
semantic structure as a hierarchy of units, defined using coarse-grained and intuitive definitions,
and consequently can be reliably annotated by non-experts, after as little as two hours
of training \cite{marinotti2014}.
Second, UCCA is a cross-linguistically applicable scheme, seeking to represent what is shared between languages,
by building on an established framework for typological description called
``Basic Linguistic Theory'' \cite[BLT]{Dixon:10a,Dixon:10b,Dixon:12},
one of the most widely used frameworks for linguistic description.
Indeed, the scheme's cross-linguistic applicability has been demonstrated through its
application to annotation in English, French, German and Czech. 
Third, the scheme has been shown to be semantically stable
in translation: UCCA annotations of translated text usually contain the same set of relationships
\cite{sulem2012}. This is an important feature for the semantic annotation, as it allows us to
assume that the semantic units of the source indeed reflect a common layer of representation that
should be preserved in translation, and so should be represented in the translation output too.
The non-stability of verbal argument structures, which may be translated to a nominal or adjectival
argument structure in another language, is one of the shortcomings of MEANT which HUME addresses.
\oa{example?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The HUME Measure}\label{sec:hume}

We do not distinguish fluency and adequacy judgements, as they are correlated anyway \cite{ccb}.

\subsection{Comparison with HMEANT}\label{sec:hmeant_comp}

For instance, consider the sentence ``A coronary angioplasty may not be technically possible'',
which was translated by one of the systems we experimented with as
``Eine koronare Angioplastie kann nicht technisch m{\"o}glich'', i.e., the main verb ``sein'' (``be'') is omitted.
While this may be interpreted is a minor error, HMEANT will assign it a very low score, as it failed to
translate the main verb.

\oa{add statistics about frequency of nominalization and copula clauses and linkers annotation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}\label{sec:experiments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conlusion}\label{sec:conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Human Semantic Evaluation}

\oa{mention TER: using insertions, deletions, substitutions and shift of the entire sentence}

\label{sec:sem-eval:human}
We focus on producing high accuracy machine translation systems, but common 
automatic MT metrics are not able to directly capture accuracy. Even previously suggested methods
for using humans to evaluate accuracy are highly problematic. We aim to  develop a human evaluation method 
which is reliable and affordable and apply it to the MT prototypes. 
%This 
The
work described
in this section relates to 
%the 
task
\emph{T5.2: Human semantic evaluation}.
% defined in the description of action.

@@

\bibliography{main}
\bibliographystyle{acl2016}
